---
title: 'Data Science for the Juvenile Court'
author: "Martin Gleason, MS"
date: "12/5/2017"
output: slidy_presentation 
---
<!-- Limit image width and height -->
<style type='text/css'>
img {
    max-height: 560px;
    max-width: 964px;
}
</style>

<!-- Center image on slide -->
<script src="http://ajax.aspnetcdn.com/ajax/jQuery/jquery-1.7.min.js"></script>
<script type='text/javascript'>
$(function() {
    $("p:has(img)").addClass('centered');
});
</script>
```{r, include= FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width="400px", dpi=120)
library("tidyverse")
library("knitr")
```
## Ubiquity, Abstraction, Absurdity
![Is this data?](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/Data_Outlook.jpg)

## Human Driven Process
![Spreadsheets are digital ledgers](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/ledger.jpg)

## Complex But Concrete
![Galton's Work on Regression to the mean. He was also a racist piece of garbage](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/Galton's_correlation_diagram_1875.jpg)

## Cloud Computing
![Complex AND Abstract](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/cloudcomputing.png)
 
## Data science, what is it?
![](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/datascience.jpg)

## Data science, what is it?
  * Data Science is the way we study the capture, storage, and transformation of data into information. 
  
  * It's that complex stuff Marty talks about all the damn time. --Toastmasters, 2017

## Data Scienctists
![Data science is an exciting discipline that allows you to turn raw data into understanding, insight, and knowledge.](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/hadley.jpg) --Hadley Wickham, PhD
  
## Data Science is  
![Using data to solve probelms](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/problemsolving.jpg)

## Data Science Tools
  * Scoping the problem
  * Collecting and cleaning the data
  * Visualizing the Data
  * Making predictions

## Data Science Heirarchy
![Like Maslow, but for data](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/pyramnid.jpg)
  
## What is Social Good?
![If we work at 1100 S Hamilton, we work for the social good](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/SocialGood.png)
  
## What is Data Science for the Social Good?
![Using data science to make the world a better place.](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/Social Good 600 v1.png)

## Data Science for the Social Good
  * Identiying problemst
  * New Solutions
  * Reproducing it to scale
  * What would Data Science for the Juvenile Court Look Like?


<style type='text/css'>
img {
    max-height: 1120px;
    max-width: 1928px;
}
</style>
## Concrete Steps: What is Visualizing our Information?
```{r, echo = F}

ggplot(iris, aes(x = Sepal.Length, y = Petal.Width, col = Species)) + geom_jitter(size = 4 ) +
 labs(x = "Sepal Length", y = "Petal Width", title = "Iris Sepal Length in Relation to Petal Width, by Species")
```
<style type='text/css'>
img {
    max-height: 560px;
    max-width: 964px;
}
</style>
## Sepal Plot
  - Shows us at a glance what the relationship is between flower parts across three species of flower
  - What does our data show us?

## Our Data, Visualized
![Based on Diversion Data from 2012-2016](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/bar_race_status.jpg)

##  Methods
  *  Tidy Data
  *  Statisical Analysis
  *  Understaning the problem

## Tools
![The code behind this presentation](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/rstudio.png)

## Data Science for the Juvenile Court
![End Game: Explaining this!](/Users/marty/Dropbox (Personal)/codingProjects/R/DataScience for the Court 101/JuvenileIntakes-byRegion.png)

  